Robust calibration of numerical models based on relative regret

### 2019-11-22 article.tex
change notation k_mean, k_var to k_E , k_V
change notation k_mean, k_var to k_E , k_V, new figs
typos

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}
\usepackage{easy-todo}
\usepackage{graphicx}
\usepackage{booktabs}
% À changer
\newcommand{\yobs}{\mathbf{y}^o}
\DeclareMathOperator*{\argmin}{arg\,min \,}
\DeclareMathOperator*{\argmax}{arg\,max \,}
\newcommand{\Var}{\mathbb{V}\textrm{ar}}
\newcommand{\Ex}{\mathbb{E}}
\newcommand{\Prob}{\mathbb{P}}
\newcommand{\Cov}{\textsf{Cov}}
\newcommand{\tra}{\mathrm{tr}}
\newcommand{\kmean}{{\mathbf{k}}_{\mathrm{mean}}}
\newcommand{\hatkmean}{\hat{\mathbf{k}}_{\mathrm{mean}}}
\newcommand{\kvar}{{\mathbf{k}}_{\mathrm{var}}}
\newcommand{\hatkvar}{\hat{\mathbf{k}}_{\mathrm{var}}}
\newcommand{\kmpe}{{\mathbf{k}}_{\mathrm{MPE}}}
\newcommand{\hatkmpe}{\hat{\mathbf{k}}_{\mathrm{MPE}}}
\newcommand{\kest}{\hat{\mathbf{k}}}

\newcommand{\checkap}{{\alpha}_p}
\newcommand{\checka}{{\alpha}}
\newcommand{\checkk}{\mathbf{k}}
\newcommand{\checkkp}{{\mathbf{k}}_p}
\newcommand{\Kspace}{\mathbb{K}}
\newcommand{\Uspace}{\mathbb{U}}
\newcommand{\JBH}{J_{\mathrm{BH}}}
\newcommand{\JBHS}{J_{\mathrm{BHswap}}}

@@

A lot of different methods are readily available to solve these
minimisation problems. For instance, stochastic Sample Approximation
\citep{juditsky_stochastic_2009,kim_guide_2015} is based on a finite
and fixed set of samples $\{ \mathbf{u}^{i}\}_{i=1 \dots N}$ of
$\mathbf{U}$.
%the sampling of a certain amount of $\mathbf{U}$ 
The estimations at a given $\mathbf{k}$ are computed using standard Monte Carlo, resulting in the following optimisation problems:
\begin{equation}
\hatkmean = \argmin_{\mathbf{k} \in \Kspace} \sum_{i=1}^N  J(\mathbf{k},\mathbf{u}^i)
\end{equation}
and
\begin{equation}
\hatkvar = \argmin_{\mathbf{k} \in \Kspace} \sum_{i=1}^N  \left( J(\mathbf{k},\mathbf{u}^i) -  \sum_{j=1}^N  J(\mathbf{k},\mathbf{u}^j) \right )^2
\end{equation}
%In the following, the hat notation will indicate an estimator. 
If computationally affordable, one can perform these estimations on a regular grid on $\Kspace \times \Uspace$. In case of expensive computer code, one can build a meta model to ease the minimisation, such as Gaussian processes \citep{janusevskis_simultaneous_2010}.
Even though $\kmean$ is a reasonable choice, there is no guarantee that $J(\kmean, \mathbf{U}=\mathbf{u})$ will not reach catastrophic level for some  $\mathbf{u}$. On the other hand, using $\kvar$ will ensure stability of the cost function, but whithout any control of its level of quality.
%
%For a single $\mathbf{k}$, the value of the cost function is controlled in a probabilistic sense by the mean and variance.
%Chebyshev's inequality gives an upper bound on the probability of being more than $\lambda>0$ units from the mean:
%\begin{equation}
%  \label{eq:cheby_ineq}
%  \Prob_{\mathbf{U}}\left[|J(\mathbf{k}% _{\mathrm{mean}}
%    ,\mathbf{U}) - \mu(\mathbf{k}% _{\mathrm{mean}}
%    )|> \lambda\right] \leq \frac{\sigma^2(\mathbf{k}% _{\mathrm{mean}}
%    )}{\lambda^2}
%\end{equation}
%
Ideally, one would want to have a small mean value, and a small variance as well. Multi-objective optimisation is a proper tool to deal with these simultaneous and sometimes concurrent objectives, for exemple by computing the Pareto front of $\left(\mu(\mathbf{k}),\sigma^2(\mathbf{k})\right)$ as done in~\cite{baudoui_optimisation_2012}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Numerical illustration}
\label{ssec:num_illu}
Before going further in the explanation of our approach, let us illustrate the nature of the 3 previously detailled estimator, $\hatkmean, \hatkvar$ and $\hatkmpe$ on two analytical cost functions. These functions are based on the Branin-Hoo's function, slightly modified to ensure strict positivity:
\begin{align}
  \label{eq:branin_hoo}
 \mathrm{BH}(x_1,x_2) &= \frac{1}{51.95}\left[\left(\bar{x}_2 - \frac{5.1 \bar{x}_1^2}{4\pi^2} + \frac{5\bar{x}_1}{\pi} -6 \right)^2 + \left(10 - \frac{10}{8\pi}\right)\cos(\bar{x}_1)-44.81\right]+2\\
&\text{with } \bar{x}_1 = 3x_1-5,\quad \bar{x}_2 = 3x_2
\end{align}
%
Using Eq.~\eqref{eq:branin_hoo}, we define the two cost functions on $\Kspace \times \Uspace = [0,5] \times [0,5]$ as:
\begin{align*} J_{\mathrm{BH}} : (\mathbf{k},\mathbf{u}) \mapsto \mathrm{BH}(\mathbf{k},\mathbf{u}) \\
J_{\mathrm{BHswap}} : (\mathbf{k},\mathbf{u}) \mapsto \mathrm{BH}(\mathbf{u},\mathbf{k})
\end{align*}
%We will continue to use $J$ as a generic notation for the cost function, when its use is not specific to the Branin-Hoo function.
Even though the functions are quite similar, the asymmetric roles of $\mathbf{k}$ and $\mathbf{u}$ cause different behaviour.

\begin{figure*}[!ht]
  \centering
  \includegraphics[width=12cm]{Figures/branin_side_moments_noscale.pdf}
  \caption{Left: Contour of the $J_{\mathrm{BH}}$ function, conditional mean and variance. The estimates $\hatkmean$ and $\hatkvar$ are plotted with the dashed line. Right: $J_{\mathrm{BHswap}}$ function. The scale of the bottom plots have not been represented.} %TODO revoir
\label{fig:branin_moments}
\end{figure*}
%\clearpage % Pour lisibilité dans le preview

@@

 The left, respectively right, column stands for $J_{\mathrm{BH}}$, respectively $J_{\mathrm{BHswap}}$ function. Functions $\mu(\mathbf{k})$ and $\sigma(\mathbf{k})$ are drawn on the bottom row, respectively in purple and green. The corresponding minimizers $\hatkmean$ and $\hatkvar$ are also plotted.
On this figure, we can observe that $\hatkmean$ and $\hatkvar$ are close for the $J_{\mathrm{BH}}$ function, while have significant different value for the $J_{\mathrm{BHswap}}$ function.
%\clearpage

Illustrations related to $\hatkmpe$ are depicted on Figure~\ref{fig:contours}. As before, the set of $\mathbf{u}^i$ is taken from a regular grid. Top row shows the contour plot of both functions as well as the set of conditional minimisers $\{\mathbf{k}_{\mathbf{u}^i}\}_{1\leq i \leq N}$ in red, as defined in Eq.~\eqref{eq:conditional_minimiser}.
The left, respectively right, column stands for $J_{\mathrm{BH}}$, respectively $J_{\mathrm{BHswap}}$ function. The bottom rows presents three approximations of the density of minimisers: the histogram in grey (bin size selected using Freedman-Diaconis from~\cite{freedman_histogram_1981}), the result of a kernel density estimation (KDE) with Gaussian kernels in red (using Scott's rule from~\cite{scott_optimal_1979} for bandwidth selection), and the estimation by a Gaussian mixture. The latter has been calculated with the EM algorithm. The number of Gaussians has been fixed to 3, a guess based on the general shape of the histogram. Respective estimations of $\hatkmpe$ are also depicted using dashed lines.

@@

\begin{figure*}
  \centering
  \includegraphics[width=12cm]{Figures/branin_side_66.pdf}
  \caption{Top Left:  $J_{\mathrm{BH}}$ function along with conditional minimisers in red. Bottom left: Estimated density using KDE and EM algorithm and conditional mean. The dashed lines indicate the MPE found using those methods. Right: Same quantities with $J_{\mathrm{BHswap}}$. The estimation of the MPE is consistent between the methods for $J_{\mathrm{BHswap}}$, but not for  $J_{\mathrm{BH}}$}
\label{fig:contours}
\end{figure*}

@@

Alternatively, we can consider the mixing coefficients of the EM
density estimation. The Gaussian centered at $1.5$ has been attributed
a weight of $0.608$, while the one centered at $3.8$ has a mixing
weight of $0.226$. Ultimately, an optimiser would be more likely to be
close to $1.5$, but we do not have information on its performance in
this region around this value.

@@

\section{Relative regret-based family of estimators}%A new family of robust estimators \elise{titre a revoir}}
\label{sec:relax_constraint}
\subsection{Taking the neighborhood into consideration}
The density of minimisers has been estimated by optimising $\mathbf{k}\mapsto J(\mathbf{k},\mathbf{u})$ over $\Kspace$ for different realisations of $\mathbf{u}$. Instead of only considering  optimal values, we propose to consider their {\it acceptable} neighbourhood in terms of performance of the cost function as well, as illustrated in Figure~\ref{fig:relax_tuto}. 
To do so, for each $\mathbf{u}$, we define as acceptable values of the cost function, the values that are below $\alpha J^*(\mathbf{u})$, with $\alpha > 1$.

@@

\begin{table*}[!h]
\centering
\caption{Estimations performed for $J_{\mathrm{BHswap}}$, sorted by value}
\label{tab:recap_estimates_BHs}
\begin{tabular}{lr} \toprule
Estimate & Value \\ \midrule
$\kest_{\mathrm{MPE}}$ & 0.606 \\ 
$\kest_{\mathrm{maxratio}},~ \hat{p}_{\mathrm{maxratio}}=0.766$ & 1.537 \\ 
$\kest_{\mathrm{mean}}$ & 1.752 \\ 
$\kest_p,~p=0.90$ & 2.112 \\ 
$\kest_p,~p=0.95$ & 2.457 \\ 
$\kest_{\mathrm{var}}$ & 2.638 \\ 
$\kest_1,~p=1$ & 2.798   \\ \bottomrule
\end{tabular}
\end{table*}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=.7\textwidth]{Figures/RobustSWEmis_plots.pdf}
\caption{Procedure of robust calibration for the shallow water problem. Top: contours of $J$, conditional minimisers and $\{(\mathbf{k},\mathbf{u}) | J(\mathbf{k},\mathbf{u}) = \hat{\alpha}_1 J^*(\mathbf{u})\}$. Middle: Conditional moments and histogram and KDE of the conditional minimisers. Bottom: $\hat{\Gamma}_{\alpha_p}$ for different levels $p$}
\label{fig:estimation_swe}
\end{figure}
\begin{table*}[!h]
\centering
\caption{Calibrated values of $\mathbf{k}$ according to different criteria}
\begin{tabular}{lr} \toprule
Estimator & Value \\ \midrule
$\hatkmpe$ & 0.249 \\
$\kest_{\mathrm{global}}$ & 0.290 \\
$\hat{\mathbf{k}}_{p},~p=1$ & 0.423 \\ 
$\hat{\mathbf{k}}_p,~p=0.90$ & 0.458 \\ 
$\hatkmean$ & 0.501 \\ 
$\hat{\mathbf{k}}_p,~p=0.80$ & 0.505 \\ 
$\hat{\mathbf{k}}_p,~p=0.70$ & 0.560 \\ 
$\hatkvar$ & 0.990\\ \bottomrule
\end{tabular}
\label{tab:recap_estimates_metaSWE}
\end{table*}
Similarly as for $\JBH$ and $\JBHS$, the profiles are depicted Figure~\ref{fig:profiles_swe}.
\begin{figure}[!h]
  \centering
  \includegraphics[width=.8\textwidth]{Figures/profile_swe}
  \caption{Profiles for the calibration problem}
\label{fig:profiles_swe}
\end{figure}
We can see that the performances of $\kest_1$ and $\hatkmean$ are very similar, but $\kest_1$ has better performances when $\mathbf{u} > 0.6$. When comparing with the global optimiser $\kest_{\mathrm{global}}$, $\kest_1$ performs better when $\mathbf{u}<0.625$. As $\mathbf{U}$ is uniformly distributed on $\Uspace=[0.5,0.7]$, we can graphically estimate that the probability that $\kest_1$ outperforms $\kest_{\mathrm{global}}$ is greater than $0.5$, that is that $\Prob_\mathbf{U}\left[J(\kest_1,\mathbf{U})<J(\kest_{\mathrm{global}},\mathbf{U})\right] > 0.5$.

>>>>

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}
\usepackage{easy-todo}
\usepackage{graphicx}
\usepackage{booktabs}
% À changer
\newcommand{\yobs}{\mathbf{y}^o}
\DeclareMathOperator*{\argmin}{arg\,min \,}
\DeclareMathOperator*{\argmax}{arg\,max \,}
\newcommand{\Var}{\mathbb{V}\textrm{ar}}
\newcommand{\Ex}{\mathbb{E}}
\newcommand{\Prob}{\mathbb{P}}
\newcommand{\Cov}{\textsf{Cov}}
\newcommand{\tra}{\mathrm{tr}}
\newcommand{\kmean}{{\mathbf{k}}_{\Ex}}
\newcommand{\hatkmean}{\hat{\mathbf{k}}_{\Ex}}
\newcommand{\kvar}{{\mathbf{k}}_{\mathbb{V}}}
\newcommand{\hatkvar}{\hat{\mathbf{k}}_{\mathbb{V}}}
\newcommand{\kmpe}{{\mathbf{k}}_{\mathrm{MPE}}}
\newcommand{\hatkmpe}{\hat{\mathbf{k}}_{\mathrm{MPE}}}
\newcommand{\kest}{\hat{\mathbf{k}}}

\newcommand{\checkap}{{\alpha}_p}
\newcommand{\checka}{{\alpha}}
\newcommand{\checkk}{\mathbf{k}}
\newcommand{\checkkp}{{\mathbf{k}}_p}
\newcommand{\hatkp}{\hat{\mathbf{k}}_p}
\newcommand{\Kspace}{\mathbb{K}}
\newcommand{\Uspace}{\mathbb{U}}
\newcommand{\JBH}{J_{\mathrm{BH}}}
\newcommand{\JBHS}{J_{\mathrm{BHswap}}}

@@

A lot of different methods are readily available to solve these
minimisation problems. For instance, stochastic Sample Approximation
\citep{juditsky_stochastic_2009,kim_guide_2015} is based on a finite
and fixed set of samples $\{ \mathbf{u}^{i}\}_{i=1 \dots N}$ of
$\mathbf{U}$.
%the sampling of a certain amount of $\mathbf{U}$ 
The estimations at a given $\mathbf{k}$ are computed using standard Monte Carlo, resulting in the following optimisation problems:
\begin{equation}
\hatkmean = \argmin_{\mathbf{k} \in \Kspace} \sum_{i=1}^N  J(\mathbf{k},\mathbf{u}^i)
\end{equation}
and
\begin{equation}
\hatkvar = \argmin_{\mathbf{k} \in \Kspace} \sum_{i=1}^N  \left( J(\mathbf{k},\mathbf{u}^i) -  \sum_{j=1}^N  J(\mathbf{k},\mathbf{u}^j) \right )^2
\end{equation}
%In the following, the hat notation will indicate an estimator. 
If computationally affordable, one can perform these estimations on a regular grid on $\Kspace \times \Uspace$. In case of expensive computer code, one can build a meta model to ease the minimisation, such as Gaussian processes \citep{janusevskis_simultaneous_2010}.
Even though $\kmean$ is a reasonable choice, there is no guarantee that $J(\kmean, \mathbf{U}=\mathbf{u})$ will not reach catastrophic level for some  $\mathbf{u}$. On the other hand, using $\kvar$ will ensure stability of the cost function, but whithout any control of its level of quality.
%
%For a single $\mathbf{k}$, the value of the cost function is controlled in a probabilistic sense by the mean and variance.
%Chebyshev's inequality gives an upper bound on the probability of being more than $\lambda>0$ units from the mean:
%\begin{equation}
%  \label{eq:cheby_ineq}
%  \Prob_{\mathbf{U}}\left[|J(\mathbf{k}% _{\Ex}
%    ,\mathbf{U}) - \mu(\mathbf{k}% _{\Ex}
%    )|> \lambda\right] \leq \frac{\sigma^2(\mathbf{k}% _{\Ex}
%    )}{\lambda^2}
%\end{equation}
%
Ideally, one would want to have a small mean value, and a small variance as well. Multi-objective optimisation is a proper tool to deal with these simultaneous and sometimes concurrent objectives, for exemple by computing the Pareto front of $\left(\mu(\mathbf{k}),\sigma^2(\mathbf{k})\right)$ as done in~\cite{baudoui_optimisation_2012}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Numerical illustration}
\label{ssec:num_illu}
Before going further in the explanation of our approach, let us illustrate the nature of previously detailed estimators, $\hatkmean, \hatkvar$ and $\hatkmpe$ on two analytical cost functions. These functions are based on the Branin-Hoo's function, slightly modified to ensure strict positivity:
\begin{align}
  \label{eq:branin_hoo}
 \mathrm{BH}(x_1,x_2) &= \frac{1}{51.95}\left[\left(\bar{x}_2 - \frac{5.1 \bar{x}_1^2}{4\pi^2} + \frac{5\bar{x}_1}{\pi} -6 \right)^2 + \left(10 - \frac{10}{8\pi}\right)\cos(\bar{x}_1)-44.81\right]+2\\
&\text{with } \bar{x}_1 = 3x_1-5,\quad \bar{x}_2 = 3x_2
\end{align}
%
Using Eq.~\eqref{eq:branin_hoo}, we define the two cost functions on $\Kspace \times \Uspace = [0,5] \times [0,5]$ as:
\begin{align*} J_{\mathrm{BH}} : (\mathbf{k},\mathbf{u}) \mapsto \mathrm{BH}(\mathbf{k},\mathbf{u}) \\
J_{\mathrm{BHswap}} : (\mathbf{k},\mathbf{u}) \mapsto \mathrm{BH}(\mathbf{u},\mathbf{k})
\end{align*}
%We will continue to use $J$ as a generic notation for the cost function, when its use is not specific to the Branin-Hoo function.
Even though the functions are quite similar, the asymmetric roles of $\mathbf{k}$ and $\mathbf{u}$ cause different behaviour.

\begin{figure*}[!ht]
  \centering
  \includegraphics[width=12cm]{Figures/branin_side_moments_noscale.pdf}
  \caption{The left column concerns the $J_{\mathrm{BH}}$ function, while the right one deals with $J_{\mathrm{BHswap}}$. Contours of both functions are plotted on the top, and curves of  $\mu(\mathbf{k})$ and $\sigma(\mathbf{k})$ are shown on the bottom (respective scales are note represented). Estimates $\hatkmean$ and $\hatkvar$ are plotted with the dashed line. } \label{fig:branin_moments}
\end{figure*}
%\clearpage % Pour lisibilité dans le preview

@@

 The left, respectively right, column stands for $J_{\mathrm{BH}}$, respectively $J_{\mathrm{BHswap}}$ function. Functions $\mu(\mathbf{k})$ and $\sigma(\mathbf{k})$ are drawn on the bottom row, respectively in purple and green. The corresponding minimizers $\hatkmean$ and $\hatkvar$ are also plotted.
On this figure, we can observe that $\hatkmean$ and $\hatkvar$ are close for the $J_{\mathrm{BH}}$ function, while being significantly different for the $J_{\mathrm{BHswap}}$ function.
%\clearpage

Similarly $\hatkmpe$ estimations are depicted on Figure~\ref{fig:contours}.  Top row shows the contour plot of both functions as well as the set of conditional minimisers $\{\mathbf{k}_{\mathbf{u}^i}\}_{1\leq i \leq N}$ in red, as defined in Eq.~\eqref{eq:conditional_minimiser}.
The bottom rows presents three approximations of the density of minimisers: the histogram in grey (bin size selected using Freedman-Diaconis from~\cite{freedman_histogram_1981}), the result of a kernel density estimation (KDE) with Gaussian kernels in red (using Scott's rule from~\cite{scott_optimal_1979} for bandwidth selection), and the estimation by a Gaussian mixture. The latter has been calculated with the EM algorithm. The number of Gaussians has been fixed to 3, a guess based on the general shape of the histogram. Respective estimations of $\hatkmpe$ are also depicted using dashed lines.

@@

\begin{figure*}
  \centering
  \includegraphics[width=12cm]{Figures/branin_side_66.pdf}
  \caption{Top Left:  $J_{\mathrm{BH}}$ function along with conditional minimisers in red. Bottom left: Estimated density using KDE and EM algorithm and conditional mean. The dashed lines indicate the MPE found using those methods. Right: Same quantities with $J_{\mathrm{BHswap}}$.}
\label{fig:contours}
\end{figure*}

@@

Alternatively, we can consider the mixing coefficients of the EM
density estimation. The Gaussian centered at $1.5$ has been attributed
a weight of $0.608$, while the one centered at $3.8$ has a mixing
weight of $0.226$. Ultimately, an optimiser would be more likely to be
close to $1.5$, but we do not have information on its performance in
this region around this value. \arthur{je ne comprends pas ce passage}

@@

\section{Relative regret-based family of estimators}%A new family of robust estimators \elise{titre a revoir}}
\label{sec:relax_constraint}
\subsection{Relaxing the optimality constraint}
The density of minimisers has been estimated by optimising $\mathbf{k}\mapsto J(\mathbf{k},\mathbf{u})$ over $\Kspace$ for different realisations of $\mathbf{u}$. Instead of only considering  optimal values, we propose to consider their {\it acceptable} neighbourhood in terms of performance of the cost function as well, as illustrated in Figure~\ref{fig:relax_tuto}. 
To do so, for each $\mathbf{u}$, we define as acceptable values of the cost function, the values that are below $\alpha J^*(\mathbf{u})$, with $\alpha > 1$.

@@

\begin{table*}[!h]
\centering
\caption{Estimations performed for $J_{\mathrm{BHswap}}$, sorted by value}
\label{tab:recap_estimates_BHs}
\begin{tabular}{lr} \toprule
Estimate & Value \\ \midrule
$\kest_{\mathrm{MPE}}$ & 0.606 \\ 
$\kest_{\mathrm{maxratio}},~ \hat{p}_{\mathrm{maxratio}}=0.766$ & 1.537 \\ 
$\hatkmean$ & 1.752 \\ 
$\kest_p,~p=0.90$ & 2.112 \\ 
$\kest_p,~p=0.95$ & 2.457 \\ 
$\hatkvar$ & 2.638 \\ 
$\kest_1,~p=1$ & 2.798   \\ \bottomrule
\end{tabular}
\end{table*}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=.7\textwidth]{Figures/RobustSWEmis_plots.pdf}
\caption{Procedure of robust calibration for the shallow water problem. Top: contours of $J$, conditional minimisers and $\{(\mathbf{k},\mathbf{u}) | J(\mathbf{k},\mathbf{u}) = \hat{\alpha}_1 J^*(\mathbf{u})\}$. Middle: Conditional moments and histogram and KDE of the conditional minimisers. Bottom: $\hat{\Gamma}_{\alpha_p}$ for different levels $p$}
\label{fig:estimation_swe}
\end{figure}
\begin{table*}[!h]
\centering
\caption{Calibrated values of $\mathbf{k}$ according to different criteria}
\begin{tabular}{lr} \toprule
Estimator & Value \\ \midrule
$\hatkmpe$ & 0.249 \\
$\kest_{\mathrm{global}}$ & 0.290 \\
$\hatkp,~p=1$ & 0.423 \\ 
$\hatkp,~p=0.90$ & 0.458 \\ 
$\hatkmean$ & 0.501 \\ 
$\hatkp,~p=0.80$ & 0.505 \\ 
$\hatkp,~p=0.70$ & 0.560 \\ 
$\hatkvar$ & 0.990\\ \bottomrule
\end{tabular}
\label{tab:recap_estimates_metaSWE}
\end{table*}
Similarly as for $\JBH$ and $\JBHS$, the profiles are depicted Figure~\ref{fig:profiles_swe}.
\begin{figure}[!h]
  \centering
  \includegraphics[width=.8\textwidth]{Figures/profile_swe}
  \caption{Profiles for the calibration problem}
\label{fig:profiles_swe}
\end{figure}
We can see that the performances of $\kest_1$ and $\hatkmean$ are very similar, but $\kest_1$ has better performances when $\mathbf{u} > 0.6$. When comparing with the global optimiser $\kest_{\mathrm{global}}$, $\kest_1$ performs better when $\mathbf{u}<0.625$. As $\mathbf{U}$ is uniformly distributed on $\Uspace=[0.5,0.7]$, we can graphically estimate that the probability that $\kest_1$ outperforms $\kest_{\mathrm{global}}$ is greater than $0.5$, that is that $\Prob_\mathbf{U}\left[J(\kest_1,\mathbf{U})<J(\kest_{\mathrm{global}},\mathbf{U})\right] > 0.5$.
